---
title: "R para Ingenier칤as y Ciencias"
author: "La Academia"
subtitle: "Tema 21 - Pr치ctica"
output:
  html_document:
    df_print: paged
---

# Gr치ficas

## Ejercicio 1

A침adir enunciado.

> [**Nota:**]{.underline} Recuerda utilizar el enfoque EPS.

## Soluci칩n

```{r}
# Ingresa tu c칩digo aqu칤 游놓
```

------------------------------------------------------------------------

## Ejercicio 2

A침adir enunciado.

> [**Nota:**]{.underline} Recuerda utilizar el enfoque EPS.

## Soluci칩n

```{r}
# Ingresa tu c칩digo aqu칤 游놓
```

------------------------------------------------------------------------

## Ejercicio 3

A침adir enunciado.

> [**Nota:**]{.underline} Recuerda utilizar el enfoque EPS.

## Soluci칩n

```{r}
# Ingresa tu c칩digo aqu칤 游놓
```

------------------------------------------------------------------------

## Ejercicio 4

A침adir enunciado.

> [**Nota:**]{.underline} Recuerda utilizar el enfoque EPS.

## Soluci칩n

```{r}
# Ingresa tu c칩digo aqu칤 游놓
```

------------------------------------------------------------------------

## Ejercicio 5

A침adir enunciado.

> [**Nota:**]{.underline} Recuerda utilizar el enfoque EPS.

## Soluci칩n

```{r}
# Ingresa tu c칩digo aqu칤 游놓
```

------------------------------------------------------------------------

## Ejercicio 6

A침adir enunciado.

> [**Nota:**]{.underline} Recuerda utilizar el enfoque EPS.

## Soluci칩n

```{r}
# Ingresa tu c칩digo aqu칤 游놓
```

------------------------------------------------------------------------

## Ejercicio 7

A침adir enunciado.

> [**Nota:**]{.underline} Recuerda utilizar el enfoque EPS.

## Soluci칩n

```{r}
# Ingresa tu c칩digo aqu칤 游놓
```

------------------------------------------------------------------------

## Ejercicio 8

A침adir enunciado.

> [**Nota:**]{.underline} Recuerda utilizar el enfoque EPS.

## Soluci칩n

```{r}
# Ingresa tu c칩digo aqu칤 游놓
```

------------------------------------------------------------------------

## Ejercicio 9

A침adir enunciado.

> [**Nota:**]{.underline} Recuerda utilizar el enfoque EPS.

## Soluci칩n

```{r}
# Ingresa tu c칩digo aqu칤 游놓
```

## Ejercicio 10

A침adir enunciado.

> [**Nota:**]{.underline} Recuerda utilizar el enfoque EPS.

## Soluci칩n

```{r}
# Ingresa tu c칩digo aqu칤 游놓
```

------------------------------------------------------------------------
